Modelling the emergence of whisker barrels

### 2020-07-04 paper/briefpaper/brief.tex
Adds note about checking on contours in movie (need to remake the movie) and also a sentence noting how the label locns are determined, which one reviewer mentioned

Movie corresponding to Fig.\,\ref{fig:main}C in the main paper. Simulation parameters were
$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\gamma\in\pm 2$,
$\epsilon=1.2$ and $\delta{t}=0.0001$. Colours indicate the thalamic
projection for which the connection density is maximal, black lines delineate
boundaries, and overlaid contours show $c>0.5$. The final frame in the movie
is step 30000 of the simulation.

>>>>

Movie corresponding to Fig.\,\ref{fig:main}C in the main paper. Simulation parameters were
\MPtwo{$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\gamma\in\pm 2$,
$\epsilon=1.2$ and $\delta{t}=0.0001$}. Colours indicate the thalamic
projection for which the connection density is maximal, black lines delineate
boundaries, and overlaid contours show $c>0.5$ \textbf{FIXME: Will need to
  check this statement after regenerating movie}. \cmnt{Barrel labels are
  always located at the centroid of their field(s).} The final frame in the movie
is step 30000 of the simulation.
